### 2025-07-13 factor-analysis.qmd
20250712 - tweaks
20250713 - tweaks

> "All models are wrong, but some are useful."
>
> --- George Box [-@Box1979, p. 202]

@@

Criteria for acceptable fit and good fit of SEM models are in @semFitIndices.
In addition, dynamic fit indexes have been proposed based on simulation to identify fit index cutoffs that are tailored to the characteristics of the specific model and data [@McNeish2023]; dynamic fit indexes are available via the `dynamic` package [@R-dynamic] or with a [webapp](https://dynamicfit.app).

>>>>

> "*All models are wrong, but some are useful.*"
>
> --- George Box [-@Box1979, p. 202]

@@

Criteria for acceptable fit and good fit of SEM models are in @tbl-semFitIndices.
In addition, dynamic fit indexes have been proposed based on simulation to identify fit index cutoffs that are tailored to the characteristics of the specific model and data [@McNeish2023]; dynamic fit indexes are available via the `dynamic` package [@R-dynamic] or with a [webapp](https://dynamicfit.app).

### 2025-07-13 machine-learning.qmd
20250712 - tweaks
20250713 - tweaks

We set up the *k* folds using the `group_vfold_cv()` function of the `rsample` package [@R-sample].

@@

We set up the LOO folds using the `loo_cv()` function of the `rsample` package [@R-sample].

>>>>

We set up the *k* folds using the `group_vfold_cv()` function of the `rsample` package [@R-rsample].

@@

We set up the LOO folds using the `loo_cv()` function of the `rsample` package [@R-rsample].
